---
title: "guest"
author: "yonghua su"
date: "3/21/2021"
output: html_document
---

# Overview

## Load libraries
We load libraries for general data wrangling and general visualisation.
```{r}
library(readr)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(grid)
library(ggridges)
library(ggExtra)
library(forecast)
library(prophet)
```

## Helper functions
```{r}
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

## Load data
```{r}
air_visits <- read_csv('air_visit_data.csv.zip', col_types = cols())
air_reserve <- read_csv('air_reserve.csv.zip', col_types = cols())
hpg_reserve <- read_csv('hpg_reserve.csv.zip', col_types = cols())
air_store <- read_csv('air_store_info.csv.zip', col_types = cols())
hpg_store <- read_csv('hpg_store_info.csv.zip', col_types = cols())
holidays <- read_csv('date_info.csv.zip', col_types = cols())
store_ids <- read_csv('store_id_relation.csv.zip', col_types = cols())
test <-read_csv('sample_submission.csv.zip', col_types = cols())
```

Let's have an overview of the data sets.

## Air visits

```{r}
summary(air_visits)
glimpse(air_visits)
air_visits %>% distinct(air_store_id) %>% nrow()
```

We find that this file contains the *visitors* numbers for each *visit\_date* and *air\_store\_id*. There are 829 different stores.

## Air Reserve

```{r}
summary(air_reserve)
glimpse(air_reserve)
air_reserve %>% distinct(air_store_id) %>% nrow()
```
We find that the *air* reservations include the *date* and *time* of the reservation, as well as those of the visit. We have reservation numbers for 314 *air* stores:

## HPG Reserve

```{r}
summary(hpg_reserve)
glimpse(hpg_reserve)
hpg_reserve %>% distinct(hpg_store_id) %>% nrow()
```


## Air Store

```{r}
summary(air_store)
glimpse(air_store)
```

We find that the *air\_store* info includes the name of the particular cuisine along with the name of the area.


## HPG Store

```{r}
summary(hpg_store)
glimpse(hpg_store)
```

There are 4690 different *hpg\_store\_ids*, which are significantly fewer than we have reservation data for.


## Holidays

```{r}
summary(holidays)
glimpse(holidays)
```

We called the *date\_info* file *holidays*, because that's essentially the information it contains. Holidays are encoded as binary flags in integer format.


## Store IDs
```{r}
summary(store_ids)
glimpse(store_ids)
```

This is a relational file that connects the *air* and *hpg* ids. There are only 150 pairs, which is less than 20% of all *air* stores.


## Test data
```{r}
summary(test)
glimpse(test)
```

The *id* of the final submission file is a concatenation of the *air\_id* and the *date*.


## Missing values

```{r}
sum(is.na(air_visits))
sum(is.na(air_reserve))
sum(is.na(hpg_reserve))
sum(is.na(air_store))
sum(is.na(hpg_store))
sum(is.na(holidays))
sum(is.na(store_ids))
sum(is.na(test))
```

There are no missing values in our data.


## Reformating features

We change the formatting of the date/time features and also reformat a few features to logical and factor variables for exploration purposes.

```{r}
air_visits <- air_visits %>%
  mutate(visit_date = ymd(visit_date))

air_reserve <- air_reserve %>%
  mutate(visit_datetime = ymd_hms(visit_datetime),
         reserve_datetime = ymd_hms(reserve_datetime))

hpg_reserve <- hpg_reserve %>%
  mutate(visit_datetime = ymd_hms(visit_datetime),
         reserve_datetime = ymd_hms(reserve_datetime))

air_store <- air_store %>%
  mutate(air_genre_name = as.factor(air_genre_name),
         air_area_name = as.factor(air_area_name))

hpg_store <- hpg_store %>%
  mutate(hpg_genre_name = as.factor(hpg_genre_name),
         hpg_area_name = as.factor(hpg_area_name))

holidays <- holidays %>%
  mutate(holiday_flg = as.logical(holiday_flg),
         date = ymd(calendar_date),
         calendar_date = as.character(calendar_date))
```

# EDA
## Air Visits
We plot the total number of visitors per day over the full *training* time range together with the median visitors per day of the week and month of the year:

```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 1", out.width="100%"}
p1 <- air_visits %>%
  group_by(visit_date) %>%
  summarise(all_visitors = sum(visitors)) %>%
  ggplot(aes(visit_date,all_visitors)) +
  geom_line(col = "blue") +
  labs(x = "All visitors", y = "Date")

p2 <- air_visits %>%
  ggplot(aes(visitors)) +
  geom_vline(xintercept = 20, color = "orange") +
  geom_histogram(fill = "blue", bins = 30) +
  scale_x_log10()

Sys.setlocale("LC_TIME", "en_US")
p3 <- air_visits %>%
  mutate(wday = wday(visit_date, label = TRUE, week_start = 1)) %>%
  group_by(wday) %>%
  summarise(visits = median(visitors)) %>%
  ggplot(aes(wday, visits, fill = wday)) +
  geom_col() +
  theme(legend.position = "none", axis.text.x  = element_text(angle=45, hjust=1, vjust=0.9)) +
  labs(x = "Day of the week", y = "Median visitors")
  
p4 <- air_visits %>%
  mutate(month = month(visit_date, label = TRUE)) %>%
  group_by(month) %>%
  summarise(visits = median(visitors)) %>%
  ggplot(aes(month, visits, fill = month)) +
  geom_col() +
  theme(legend.position = "none") +
  labs(x = "Month", y = "Median visitors")

layout <- matrix(c(1,1,1,1,2,3,4,4),2,4,byrow=TRUE)
multiplot(p1, p2, p3, p4, layout=layout)
```

- There is an interesting long-term step structure in the overall time series. This might be related to new restaurants being added to the data base. 

- The number of guests per visit per restaurant per day peaks at around 20 (the orange line).

- Friday and the weekend appear to be the most popular days; which is to be expected. Monday and Tuesday have the lowest numbers of average visitors.

- Dec appears to be the most popular month for restaurant visits. The period of Mar - May is consistently busy.

## Air Reservations
We start with the *air* restaurants and visualise their visitor volume through reservations for each day, with the hours of these visits and the time between making a reservation and visiting the restaurant:
```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 3", out.width="100%"}
foo <- air_reserve %>%
  mutate(reserve_date = date(reserve_datetime),
         reserve_hour = hour(reserve_datetime),
         reserve_wday = wday(reserve_datetime, label = TRUE, week_start = 1),
         visit_date = date(visit_datetime),
         visit_hour = hour(visit_datetime),
         visit_wday = wday(visit_datetime, label = TRUE, week_start = 1),
         diff_hour = time_length(visit_datetime - reserve_datetime, unit = "hour"),
         diff_day = time_length(visit_datetime - reserve_datetime, unit = "day")
         )

p1 <- foo %>%
  group_by(visit_date) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(visit_date, all_visitors)) +
  geom_line() +
  labs(x = "'air' visit date")

p2 <- foo %>%
  group_by(visit_hour) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(visit_hour, all_visitors)) +
  geom_col(fill = "blue")

p3 <- foo %>%
  filter(diff_hour < 24*5) %>%
  group_by(diff_hour) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(diff_hour, all_visitors)) +
  geom_col(fill = "blue") +
  labs(x = "Time from reservation to visit [hours]")

layout <- matrix(c(1,1,2,3),2,2,byrow=TRUE)
multiplot(p1, p2, p3, layout=layout)
```

- There were much fewer reservations made in 2016 through the *air* system; The volume only increased during the end of that year. In 2017 the visitor numbers stayed strong. 

- Reservations are made typically for the dinner *hours* in the evening.

- The most popular strategy is to reserve a couple of hours before the visit, but if the reservation is made more in advance then it seems to be common to book a table in the evening for one of the next evenings. 


## HPG Reservations

```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 4", out.width="100%"}
foo <- hpg_reserve %>%
  mutate(reserve_date = date(reserve_datetime),
         reserve_hour = hour(reserve_datetime),
         visit_date = date(visit_datetime),
         visit_hour = hour(visit_datetime),
         diff_hour = time_length(visit_datetime - reserve_datetime, unit = "hour"),
         diff_day = time_length(visit_datetime - reserve_datetime, unit = "day")
         )

p1 <- foo %>%
  group_by(visit_date) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(visit_date, all_visitors)) +
  geom_line() +
  labs(x = "'hpg' visit date")

p2 <- foo %>%
  group_by(visit_hour) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(visit_hour, all_visitors)) +
  geom_col(fill = "red")

p3 <- foo %>%
  filter(diff_hour < 24*5) %>%
  group_by(diff_hour) %>%
  summarise(all_visitors = sum(reserve_visitors)) %>%
  ggplot(aes(diff_hour, all_visitors)) +
  geom_col(fill = "red") +
  labs(x = "Time from reservation to visit [hours]")

layout <- matrix(c(1,1,2,3),2,2,byrow=TRUE)
multiplot(p1, p2, p3, layout=layout)
```

- Here the visits after reservation follow a more orderly pattern, with a clear spike in Dec 2016. 

- It's worth noting that here the last few hours before the visit don't see more volume than the 24 or 48 hours before. This is in stark constrast to the *air* data.


## Air Store

```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 6", out.width="100%"}
p1 <- air_store %>%
  group_by(air_genre_name) %>%
  count() %>%
  ggplot(aes(reorder(air_genre_name, n, FUN = min), n, fill = air_genre_name)) +
  geom_col() +
  coord_flip() +
  theme(legend.position = "none") +
  labs(x = "Type of cuisine (air_genre_name)", y = "Number of air restaurants")
  
p2 <- air_store %>%
  group_by(air_area_name) %>%
  count() %>%
  ungroup() %>%
  top_n(15,n) %>%
  ggplot(aes(reorder(air_area_name, n, FUN = min) ,n, fill = air_area_name)) +
  geom_col() +
  theme(legend.position = "none") +
  coord_flip() +
  labs(x = "Top 15 areas (air_area_name)", y = "Number of air restaurants")

layout <- matrix(c(1,2),2,1,byrow=TRUE)
multiplot(p1, p2, layout=layout)
```

## HPG Store
```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 8", out.width="100%"}
p1 <- hpg_store %>%
  group_by(hpg_genre_name) %>%
  count() %>%
  ggplot(aes(reorder(hpg_genre_name, n, FUN = min), n, fill = hpg_genre_name)) +
  geom_col() +
  coord_flip() +
  theme(legend.position = "none") +
  labs(x = "Type of cuisine (hpg_genre_name)", y = "Number of hpg restaurants")
  
p2 <- hpg_store %>%
  mutate(area = str_sub(hpg_area_name, 1, 20)) %>%
  group_by(area) %>%
  count() %>%
  ungroup() %>%
  top_n(15,n) %>%
  ggplot(aes(reorder(area, n, FUN = min) ,n, fill = area)) +
  geom_col() +
  theme(legend.position = "none") +
  coord_flip() +
  labs(x = "Top 15 areas (hpg_area_name)", y = "Number of hpg restaurants")

layout <- matrix(c(1,2),1,2,byrow=TRUE)
multiplot(p1, p2, layout=layout)
```

## Holidays

```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 9", out.width="100%"}
foo <- holidays %>%
  mutate(wday = wday(date, week_start = 1))

p1 <- foo %>%
  ggplot(aes(holiday_flg, fill = holiday_flg)) +
  geom_bar() +
  theme(legend.position = "none")
p1
```



# Feature relations
## Visitors per genre

```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 11", out.width="100%"}
foo <- air_visits %>%
  left_join(air_store, by = "air_store_id")

foo %>%
  group_by(visit_date, air_genre_name) %>%
  summarise(mean_visitors = mean(visitors)) %>%
  ungroup() %>%
  ggplot(aes(visit_date, mean_visitors, color = air_genre_name)) +
  geom_line() +
  labs(y = "Average number of visitors to 'air' restaurants", x = "Date") +
  theme(legend.position = "none") +
  scale_y_log10() +
  facet_wrap(~ air_genre_name)
```

- The mean values range between 10 and 100 visitors per genre per day. Within each category, the long-term trend looks reasonably stable. There is an upward trend for "Creative Cuisine" and "Okonomiyaki" et al., while the popularity of "Asian" food has been declining since late 2016. 

- The low-count time series like "Karaoke" or "Asian" are understandably more noisy than the genres with higher numbers of visitors. Still, "Asian" restaurants appear to be very popular despite (or because of?) their rarity.


```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 12", out.width="100%"}
p1 <- foo %>%
  mutate(wday = wday(visit_date, label = TRUE, week_start = 1)) %>%
  group_by(wday, air_genre_name) %>%
  summarise(mean_visitors = mean(visitors)) %>%
  ggplot(aes(air_genre_name, mean_visitors, color = wday)) +
  geom_point(size = 4) +
  theme(legend.position = "left", axis.text.y = element_blank(),
        plot.title = element_text(size = 14)) +
  coord_flip() +
  labs(x = "") +
  scale_x_discrete(position = "top") +
  ggtitle("air_genre_name") +
  scale_color_hue()

p2 <- foo %>%
  ggplot(aes(visitors, air_genre_name, fill = air_genre_name)) +
  geom_density_ridges(bandwidth = 0.1) +
  scale_x_log10() +
  theme(legend.position = "none") +
  labs(y = "") +
  scale_fill_cyclical(values = c("blue", "red"))

layout <- matrix(c(1,1,2,2,2),1,5,byrow=TRUE)
multiplot(p1, p2, layout=layout)
p1 <- 1; p2 <- 1; p3 <- 1; p4 <- 1; p5 <- 1
```

- The biggest difference between weekend and weekdays exists for the "Karaoke" bars, which rule the weekend. A similar trend, although with a considerably smaller gap, can be seen for the "International" cuisine.

- No *genre* really goes against the trend of busier weekends. The smallest variations are in the generic "Other" category, the "Japanese" food, and also the "Korean" cuisine which is the only category where Fridays are the busiest days. General "Bars/Cocktail" are notably unpopular overall.

- The density curves confirm the impression we got from the week-day distribution: the "Asian" restaurants have rarely less than 10 visitors per date and the "Karaoke" places show a very broad distribution due to the strong impact of the weekends. Note the logarithmic x-axis.



## The impact of holidays

```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 13", fig.height=3.5, out.width="100%"}
foo <- air_visits %>%
  mutate(calendar_date = as.character(visit_date)) %>%
  left_join(holidays, by = "calendar_date")

p1 <- foo %>%
  ggplot(aes(holiday_flg, visitors, color = holiday_flg)) +
  geom_boxplot() +
  scale_y_log10() +
  theme(legend.position = "none")

p2 <- foo %>%
  mutate(wday = wday(date, label = TRUE, week_start = 1)) %>%
  group_by(wday, holiday_flg) %>%
  summarise(mean_visitors = mean(visitors)) %>%
  ggplot(aes(wday, mean_visitors, color = holiday_flg)) +
  geom_point(size = 4) +
  theme(legend.position = "none") +
  labs(y = "Average number of visitors")

layout <- matrix(c(1,2),1,2,byrow=TRUE)
multiplot(p1, p2, layout=layout)
```


- Overall, holidays don't have any impact on the average visitor numbers (left panel). As so often, more information is hidden in the details.

- While a weekend holiday has little impact on the visitor numbers, and even decreases them slightly, there is a much more pronounced effect for the weekdays; especially Monday and Tuesday (right panel).


## Reservations vs Visits

```{r}
foo <- air_reserve %>%
  mutate(visit_date = date(visit_datetime)) %>%
  group_by(air_store_id,visit_date) %>%
  summarise(reserve_visitors_air = sum(reserve_visitors))
  
bar <- hpg_reserve %>%
  mutate(visit_date = date(visit_datetime)) %>%
  group_by(hpg_store_id,visit_date) %>%
  summarise(reserve_visitors_hpg = sum(reserve_visitors)) %>%
  inner_join(store_ids, by = "hpg_store_id")

all_reserve <- air_visits %>%
  inner_join(foo, by = c("air_store_id", "visit_date")) %>%
  inner_join(bar, by = c("air_store_id", "visit_date")) %>%
  mutate(reserve_visitors = reserve_visitors_air + reserve_visitors_hpg)
```


```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 19", out.width="100%"}
p <- all_reserve %>%
  filter(reserve_visitors < 120) %>%
  ggplot(aes(reserve_visitors, visitors)) +
  geom_point(color = "black", alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0, color = "grey60") +
  geom_smooth(method = "lm", color = "blue")
ggMarginal(p, type="histogram", fill = "blue", bins=50)
```


- The histograms show that the *reserve\_visitors* and *visitors* numbers peak below ~20 and are largely confined to the range below 100.

- The scatter points fall largely above the line of identity, indicating that there were more *visitors* that day than had reserved a table. This is not surprising, since a certain number of people will always be walk-in customers.

- A notable fraction of the points is below the line, which probably indicates that some people made a reservation but changed their mind and didn't go. That kind of effect is probably to be expected and taking it into account will be one of the challenges in this competition.

- The linear fit suggests a trend in which larger numbers of *reserve\_visitors* are more likely to underestimate the eventual *visitor* numbers. This is not surprising either, since I can imagine that it is more likely that (a) a large reservation is cancelled than (b) a large group of people walk in a restaurant without reservation.


```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 21", fig.height=3, out.width="100%"}
all_reserve %>%
  mutate(date = visit_date) %>%
  left_join(holidays, by = "date") %>%
  ggplot(aes(visitors - reserve_visitors, fill = holiday_flg)) +
  geom_density(alpha = 0.5)
```


- There are somewhat higher numbers of *visitors* compared to *reservations* on a holiday. The peaks are almost identical, but we see small yet clear differences towards larger numbers.







# Forecasting methods
## ARIMA / auto.arima


```{r}
air_id = "air_ba937bf13d40fb24"
```


```{r}
pred_len <- test %>%
  separate(id, c("air", "store_id", "date"), sep = "_") %>%
  distinct(date) %>%
  nrow()
```

```{r}  
max_date <- max(air_visits$visit_date)
split_date <- max_date - pred_len
all_visits <- tibble(visit_date = seq(min(air_visits$visit_date), max(air_visits$visit_date), 1))
```


```{r}
foo <- air_visits %>%
  filter(air_store_id == air_id)

visits <- foo %>%
  right_join(all_visits, by = "visit_date") %>%
  mutate(visitors = log1p(visitors)) %>%
  replace_na(list(visitors = median(log1p(foo$visitors)))) %>%
  rownames_to_column()
```
  

```{r}
visits_train <- visits %>% filter(visit_date <= split_date)
visits_valid <- visits %>% filter(visit_date > split_date)
```


```{r}
arima.fit <- auto.arima(tsclean(ts(visits_train$visitors, frequency = 7)),
                        stepwise = FALSE, approximation = FALSE)
```

```{r}
arima_visits <- arima.fit %>% forecast(h = pred_len, level = c(50,95))
```


```{r split=FALSE, fig.align = 'default', warning = FALSE, fig.cap ="Fig. 31", out.width="100%"}
arima_visits %>%
  autoplot +
  geom_line(aes(as.integer(rowname)/7, visitors), data = visits_valid, color = "grey40") +
  labs(x = "Time [weeks]", y = "log1p visitors vs auto.arima predictions")
```

We find that the first days of the forecast fit quite well, but then our prediction is not able to capture the larger spikes. Still, it's a useful starting point to compare other methods to.


```{r}
plot_auto_arima_air_id <- function(air_id){

  pred_len <- test %>%
    separate(id, c("air", "store_id", "date"), sep = "_") %>%
    distinct(date) %>%
    nrow()

  max_date <- max(air_visits$visit_date)
  split_date <- max_date - pred_len
  all_visits <- tibble(visit_date = seq(min(air_visits$visit_date), max(air_visits$visit_date), 1))
  
  foo <- air_visits %>%
    filter(air_store_id == air_id)

  visits <- foo %>%
    right_join(all_visits, by = "visit_date") %>%
    mutate(visitors = log1p(visitors)) %>%
    replace_na(list(visitors = median(log1p(foo$visitors)))) %>%
    rownames_to_column()
  
  visits_train <- visits %>% filter(visit_date <= split_date)
  visits_valid <- visits %>% filter(visit_date > split_date)

  arima.fit <- auto.arima(tsclean(ts(visits_train$visitors, frequency = 7)),
                          stepwise = FALSE, approximation = FALSE)

  arima_visits <- arima.fit %>% forecast(h = pred_len, level = c(50,95))

  arima_visits %>%
    autoplot +
    geom_line(aes(as.integer(rowname)/7, visitors), data = visits_valid, color = "grey40") +
    labs(x = "Time [weeks]", y = "log1p visitors vs forecast")
}
```

```{r fig.align = 'default', warning = FALSE, fig.cap ="Fig. 31", out.width="100%"}
p1 <- plot_auto_arima_air_id("air_f3f9824b7d70c3cf")
p2 <- plot_auto_arima_air_id("air_8e4360a64dbd4c50")
p3 <- plot_auto_arima_air_id("air_1c0b150f9e696a5f")
p4 <- plot_auto_arima_air_id("air_900d755ebd2f7bbd")

layout <- matrix(c(1,2,3,4),2,2,byrow=TRUE)
multiplot(p1, p2, p3, p4, layout=layout)
```

- The two time series' in the upper panels are reasonable complete, but we see that the long gaps (and our median filling) lead to problems in the predictions in the upper left panel where we loose the weekly periodicity. The upper right panel retains this periodicity and the predictions for the first days are relatively decent, but then we quickly under-predict the amplitude of the variations.

- The lower panels include two of the outliers from our time-series parameter space above; and here we see cases where things go really wrong. These kind of peculiar time series could lead to a bad performance for any otherwise decent forecasting algorithm if they contain a large enough fraction of visits in the test data set.

## Prophet

```{r message=FALSE, error=FALSE}
air_id = "air_ba937bf13d40fb24"

pred_len <- test %>%
  separate(id, c("air", "store_id", "date"), sep = "_") %>%
  distinct(date) %>%
  nrow()

max_date <- max(air_visits$visit_date)
split_date <- max_date - pred_len
all_visits <- tibble(visit_date = seq(min(air_visits$visit_date), max(air_visits$visit_date), 1))

foo <- air_visits %>%
  filter(air_store_id == air_id)

visits <- foo %>%
  right_join(all_visits, by = "visit_date") %>%
  mutate(visitors = log1p(visitors)) %>%
  rownames_to_column() %>%
  select(y = visitors,
         ds = visit_date)

visits_train <- visits %>% filter(ds <= split_date)
visits_valid <- visits %>% filter(ds > split_date)
```


```{r}
proph <- prophet(visits_train, changepoint.prior.scale=0.5, yearly.seasonality=FALSE, daily.seasonality = FALSE)
future <- make_future_dataframe(proph, periods = pred_len)
fcast <- predict(proph, future)
```


```{r fig.align = 'default', warning = FALSE, fig.cap ="Fig. 32", out.width="100%"}
plot(proph, fcast)
```

```{r fig.align = 'default', warning = FALSE, fig.cap ="Fig. 33", out.width="100%"}
prophet_plot_components(proph, fcast)
```

- Prophet detects a weekly variation pattern which is similar to what we had found before, in that Fri/Sat are more popular than the rest of the week. 
```{r}
plot_prophet_air_id <- function(air_id){
  
  pred_len <- test %>%
    separate(id, c("air", "store_id", "date"), sep = "_") %>%
    distinct(date) %>%
    nrow()

  max_date <- max(air_visits$visit_date)
  split_date <- max_date - pred_len
  all_visits <- tibble(visit_date = seq(min(air_visits$visit_date), max(air_visits$visit_date), 1))

  foo <- air_visits %>%
    filter(air_store_id == air_id)

  visits <- foo %>%
    right_join(all_visits, by = "visit_date") %>%
    mutate(visitors = log1p(visitors)) %>%
    rownames_to_column() %>%
    select(y = visitors,
          ds = visit_date)

  visits_train <- visits %>% filter(ds <= split_date)
  visits_valid <- visits %>% filter(ds > split_date)
  
  proph <- prophet(visits_train, changepoint.prior.scale=0.5,
                   yearly.seasonality=FALSE, daily.seasonality = FALSE)
  future <- make_future_dataframe(proph, periods = pred_len)
  fcast <- predict(proph, future)
  
  p <- fcast %>%
    as.tibble() %>%
    mutate(ds = date(ds)) %>%
    ggplot(aes(ds, yhat)) +
    geom_ribbon(aes(x = ds, ymin = yhat_lower, ymax = yhat_upper), fill = "light blue") +
    geom_line(colour = "blue") +
    geom_line(data = visits_train, aes(ds, y), colour = "black") +
    geom_line(data = visits_valid, aes(ds, y), colour = "grey50") +
    labs(title = str_c("Prophet for ", air_id))
  
  return(p)
}  
```


```{r results="hide", fig.align = 'default', warning = FALSE, fig.cap ="Fig. 35", out.width="100%"}
p1 <- plot_prophet_air_id("air_f3f9824b7d70c3cf")
p2 <- plot_prophet_air_id("air_8e4360a64dbd4c50")
p3 <- plot_prophet_air_id("air_1c0b150f9e696a5f")
p4 <- plot_prophet_air_id("air_820d1919cbecaa0a")

layout <- matrix(c(1,2,3,4),2,2,byrow=TRUE)
multiplot(p1, p2, p3, p4, layout=layout)
```

Looks like we're overestimating the trend component, which could probably use less flexibility, for at least three of these. The forth time series has too little data for prophet to be able to do much.

```{r}
plot_prophet_air_id_holiday <- function(air_id, use_hday){
  
  air_visits_cut <- air_visits %>%
    filter(visit_date <= ymd("20160531"))
  
  hday <- holidays %>%
    filter(holiday_flg == TRUE) %>%
    mutate(holiday = "holiday") %>%
    select(ds = date, holiday)
  
  pred_len <- test %>%
    separate(id, c("air", "store_id", "date"), sep = "_") %>%
    distinct(date) %>%
    nrow()

  max_date <- max(air_visits_cut$visit_date)
  split_date <- max_date - pred_len
  all_visits <- tibble(visit_date = seq(min(air_visits_cut$visit_date), max(air_visits_cut$visit_date), 1))

  foo <- air_visits_cut %>%
    filter(air_store_id == air_id)

  visits <- foo %>%
    right_join(all_visits, by = "visit_date") %>%
    mutate(visitors = log1p(visitors)) %>%
    rownames_to_column() %>%
    select(y = visitors,
          ds = visit_date)

  visits_train <- visits %>% filter(ds <= split_date)
  visits_valid <- visits %>% filter(ds > split_date)
  
  if (use_hday == TRUE){
    proph <- prophet(visits_train,
                     changepoint.prior.scale=0.5,
                     yearly.seasonality=FALSE,
                     daily.seasonality=FALSE,
                     holidays = hday)
    ptitle = "Prophet (w/ holidays) for "
  } else {
     proph <- prophet(visits_train,
                     changepoint.prior.scale=0.5,
                     yearly.seasonality=FALSE,
                     daily.seasonality = FALSE)
    ptitle = "Prophet for "
  }
  
  future <- make_future_dataframe(proph, periods = pred_len)
  fcast <- predict(proph, future)
  
  p <- fcast %>%
    as.tibble() %>%
    mutate(ds = date(ds)) %>%
    ggplot(aes(ds, yhat)) +
    geom_ribbon(aes(x = ds, ymin = yhat_lower, ymax = yhat_upper), fill = "light blue") +
    geom_line(colour = "blue") +
    geom_line(data = visits_train, aes(ds, y), colour = "black") +
    geom_line(data = visits_valid, aes(ds, y), colour = "grey50") +
    labs(title = str_c(ptitle, air_id))
  
  return(p)
}  
```


```{r results="hide", fig.align = 'default', warning = FALSE, fig.cap ="Fig. 36", out.width="100%"}
p1 <- plot_prophet_air_id_holiday("air_5c817ef28f236bdf", TRUE)
p2 <- plot_prophet_air_id_holiday("air_5c817ef28f236bdf", FALSE)

layout <- matrix(c(1,2),2,1,byrow=TRUE)
multiplot(p1, p2, layout=layout)
```

- There is a subtle improvement in fitting the Golden Week *visitors* when including holidays. The performance of this component might improve if there are more holidays included in the *training* set.








